Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-05-16 doc/PRF2022/PRF_main.tex
1st push yny
updates

%Title of paper
\title{Collective behavior of Suspended Janus Particles via an Integral Equation Method}

% repeat the \author .. \affiliation  etc. as needed
% \email, \thanks, \homepage, \altaffiliation all apply to the current
% author. Explanatory text should go in the []'s, actual e-mail
% address or url should go in the {}'s for \email and \homepage.
% Please use the appropriate macro foreach each type of information

@@

\begin{abstract}
% insert abstract here
\end{abstract}

@@

\subsection{}

>>>>

%Title of paper
\title{Collective behavior of Janus Particles  Suspended in a Viscous Fluid}

% repeat the \author .. \affiliation  etc. as needed
% \email \thanks, \homepage, \altaffiliation all apply to the current
% author. Explanatory text should go in the []'s, actual e-mail
% address or url should go in the {}'s for \email and \homepage.
% Please use the appropriate macro foreach each type of information

@@

\begin{abstract}
% insert abstract here

{\bf To do list:}

Unbouned Flow: 
\begin{enumerate}
\item $N_b=60$ self-assembly/relaxation runs with all 3 boundary conditions using $N=24$ points per particle (FIG. 2). Energy profiles in a linear-log plot (FIG. 3) ($E(t)$ or $\Delta E(t)$ v.s. time).

\item $N_b=198$ relaxation runs with all 3 boundary conditions using $N=24$ points per particle.
Add energy profiles to check local/absolute minimum.

\item $N_b=60$ structures in a shear flow: For both boundary conditions, lamellar (FIG. 4) and polar (FIG. 4), check convergence using $N=16$ and $N=24$. 
Compare the new results with the current FIG 4. (d). Revise FIG. 5 with more details.

\item Use particle/checker board alignment to identify the critical shear rate for phase separation.

\item $N_b=60$ structures in a Taylor-Green flow (FIG. 7-8). Add more frames for further comparison between values of flow strength $V_0$.
\end{enumerate}

Channel Flow: 
\begin{enumerate}
\item $Nb_25$ vesicle in a narrow channel.
\item $Nb_40$ multi-lamellar structure in a narrow channel.
\end{enumerate}

\end{abstract}

@@
